---
output: pdf_document
---
#NAnal - Example

**Author:** Mike Kuklinski  
**Date:** 5/24/16  
**Language:** R  
**Computer:** Windows 10, 64-bit  
**Description:** Walk through functions using an example data frame with NA values  

I begin by sourcing the NAnal functions
```{r}
suppressMessages(source('NAnal.R'))
```

Source file contains `df_test`, an example data frame
```{r}
df_test

# Percent NA
orig_na_percent <- round(sum(is.na(df_test))/(nrow(df_test)*ncol(df_test)), 2)
orig_na_percent
```

\newpage
# NAnal.var2ans   

`NAnal.var2ans` will return a table showing the correlation, percent NA, and pvalue associated
with each predictor variable.

```{r}
# Using suppresswarnings() because df_test has 'essentially perfect fit' values compared to answer variable
df_var2ans <- suppressWarnings(NAnal.var2ans(df_test, 'ans'))
df_var2ans
```

\newpage
# NAnal.reduce_comb  

`NAnal.reduce_comb` returns a list of every possible index combination by which the original 
data frame could be subset by complete cases.

```{r}
df_reduce_combs <- NAnal.reduce_comb(df_test)
# Number of combinations
length(df_reduce_combs$lists)
head(df_reduce_combs$lists,10)
```

\newpage
# NAnal.score  

`NAnal.score` runs through the list of index combinations provided by `NAnal.reduce_comb`
and provides the following information for each resulting subset data frame:  

Table Output names:  
- AdjVarIdx - Data frame indices being subset by  
- ADJVarNames - Data frame variable names associated with the indices  
- NumberObs - Number of remaining observations  
- PercentCC - Percent of complete cases  
- PercentNA - Percent NA remaining  
- Wt_Vote - Weight Score of subset Data frame  

I set `min_vote_count` equal to 6. This just means that when scoring the combinations, I'd
like to give more weight to resulting data frames with 6 or more observations.
```{r}
df_scores <- NAnal.score(df_test, df_reduce_combs$lists, 6)
head(df_scores, 30)
```

\newpage
# NAnal.score - continued  

Looking over the scores, I can see that by subsetting the original data frame by complete cases of variable `o`,
I'll get 3 rows/observations but reduce the NA percent to 8% respectively.

```{r}
# Get list of index combinations
reduce_idx_list <- df_scores$AdjVarIdx 
# Identify the first combination (associated with 'o')
idx_num <- grep('^o$',df_scores$ADJVarNames)
# Get indices as a list
reduce_idx <- lapply(str_split(as.character(reduce_idx_list[idx_num]), pattern = ' '), as.integer)
reduce_idx
# Subset original data frame by complete cases of indices
new_df <- df_test[complete.cases(df_test[,reduce_idx[[1]]]),]    
new_df
```
Similarly, I see that if I subset by complete cases of `c p`, I get 6 rows/observations and 12% NA.
```{r}
# Identify the first combination (associated with 'c')
idx_num <- grep('^c p$',df_scores$ADJVarNames)
# Get indices as a list
reduce_idx <- lapply(str_split(as.character(reduce_idx_list[idx_num]), pattern = ' '), as.integer)
reduce_idx
# Subset original data frame by complete cases of indices
new_df <- df_test[complete.cases(df_test[,reduce_idx[[1]]]),]    
new_df
```
Once you're satisfied with the ratio between the number of observations and percent NA, I would recommend using 
`na.roughfix()` or `rfImpute()`  from the `randomforest` package to fill in the remaining NA values.  






